\section{Conclusion}

We described a collection of \gls{RP} models of varying levels of complexity, then examined the differences in short-term orbital effects of \gls{RP} on \gls{LRO} between these models. Solar radiation follows a simple inverse square law, while the Moon has to be discretized into panels to evaluate lunar thermal and albedo variations. Thermal radiation dominates, and a constant albedo distribution is both sufficient and computationally cheaper than the spherical harmonics expansion \gls{DLAM1}. Large differences exist between the representations of \gls{LRO} as a cannonball and a paneled target: due to the cannonball's symmetry, accelerations do not cancel over an orbit and are generally smaller than those of a paneled target, which can have the solar array track the Sun. There are also large seasonal differences in the \gls{RP} accelerations: for small $\beta$ (e.g., around September), the accelerations are mainly radial and along-track, while they are predominantly cross-track for $\beta \approx \pm \ang{90}$ (e.g., around June). After 2.5 days, the position diverged from the no-\gls{RP} baseline by up to \qty{1100}{\m} in June and \qty{80}{\m} in September. Periodic variations of up to \qty{50}{\m} are superimposed on the secular differences over the orbit. In September, the periodic variations are damped by lunar accelerations that oppose solar accelerations.

Our results showed that \gls{RP} is essential for precise orbit determination of the \gls{LRO}. Both the total and radial accuracy requirements would be violated otherwise. However, not all models are worth the computational effort. We recommend the following setup:
\begin{itemize}
    \item Solar radiation should be included since it is cheap and important.
    \item Lunar thermal and constant albedo radiation should be included since it only increases walltime duration by \qty{20}{\percent} and affects secular and periodic variations significantly. To reduce the performance impact, fewer rings could be used, although the lunar irradiance will then be underestimated.
    \item The spatially varying albedo distribution from \gls{DLAM1} does not increase the accuracy much even though it adds a performance penalty of \qty{80}{\percent}. Therefore, it should not be included unless the utmost accuracy is desired (particularly in September). The spherical harmonics expansion could also be truncated to improve performance.
    \item The paneled target should be included since the cannonball underestimates accelerations and does not account for Sun tracking of the solar array. The performance impact of the paneled target is negligible.
    \item The cannonball target should only be used if its coefficient is estimated since a constant coefficient cannot represent changes in geometry and orientation. Even then, consistent estimation of the coefficient is problematic at small $\beta$~\cite{Slojkowski2014}.
\end{itemize}

While we restricted our investigation to a small number of models, the short-term orbital effect of these more involved models should also be investigated:
\begin{itemize}
    \item Moon topography can advance eclipse onset by up to \qty{480}{\s} for $\beta > \ang{70}$~\cite{Mazarico2018}. The conical shadow model should be replaced by one that evaluates lines of sight based on topography.
    \item Self-shadowing, particularly for solar radiation, can reduce the effective cross-section by up to \qty{40}{\percent} for large $\beta$~\cite{Mazarico2018}.
    \item \gls{DLAM1} was published in 1999 based on miscalibrated Clementine imagery, which overestimates the actual albedo. A new spherical harmonics model should be fitted from more recent imagery.
    \item Acceleration due to thermal reradiation by the spacecraft itself can be significant. Our model of instantaneous reradiation should be replaced by one that accounts for heating and conduction.
    \item The lunar opposition effect increases albedo radiation for low phase angles much more than Lambertian reflectance predicts, which becomes relevant for small $\beta$. The Hapke \gls{BRDF} with spatially resolved parameter maps~\cite{Sato2014} should be used for albedo reflection.
    \item Post-sunset lunar thermal radiation is underestimated because gradual cooling to nighttime temperatures is not reflected in our thermal model. It should be replaced with a more physical model due to the large magnitude of thermal compared to albedo radiation.
\end{itemize}



\FloatBarrier

