\documentclass{sagej}

\runninghead{Short-term orbital effects of radiation pressure on the Lunar Reconnaissance Orbiter}
\title{Short-term orbital effects of radiation pressure \\ on the Lunar Reconnaissance Orbiter}
\author{Dominik Stiller}
\affiliation{B.Sc. student, Faculty of Aerospace Engineering, Delft University of Technology, The Netherlands}
% \email{dstiller@uw.edu}
\keywords{Radiation pressure, Lunar Reconnaissance Orbiter, precision orbit determination, force modeling}


\makeglossaries
\input{acronyms}


\begin{abstract}
    Precision orbit determination for geodetic applications requires force models even for small perturbations. Radiation from the Sun and Moon is a significant source of perturbation in lunar orbits and inadequate modeling of \gls{RP} can lead to large position errors. This paper describes the short-term effect of \gls{RP} on the \gls{LRO}, which has a position knowledge requirement of 50 m to 100 m in total and below 1 m radially. We compared models of varying complexity to determine the benefits and computational cost of high-accuracy \gls{RP} modeling. We found that
    \begin{enumerate*}[label=(\arabic*)]
        \item the accelerations differ greatly depending on the Sun position,
        \item only a paneled spacecraft model can account properly for changing orientation and geometry of \gls{LRO}, and
        \item a constant-albedo model is sufficient for lunar radiation, which is dominated by the thermal component. A spherical harmonics model for lunar albedo increases computational cost with little gain in the attained accuracy.
    \end{enumerate*}
    If \gls{RP} is neglected, the along-track position errors can be as large as 1100 m and the radial error varies periodically with an amplitude of up to 24 m, highlighting the importance of adequate force modeling to meet LRO's orbit determination requirements.
\end{abstract}




\begin{document}


\maketitle

\printacronyms[style=inline,title={Abbreviations}]



\input{sections/Introduction}
\input{sections/General_models}
\input{sections/LRO_models}
\input{sections/Results}
\input{sections/Conclusion}

\begin{codeav}
The code is available at \url{https://github.com/DominikStiller/tudelft-hpb-project}.
\end{codeav}


\printbibliography

\end{document}
